\documentclass{llncs}
\usepackage{epsf}
\input{ps-fig.tex}

\begin{document}

\title{Semantic Web: Project documentation}

\author{
Marc Kirchmann and Sebastian Leitz}
\institute{Cooperative State University Baden-Wuerttemberg\\
           Master Computer Science\\
           minf010@cas.dhbw.de, minf11@cas.dhbw.de}

\maketitle

\begin{abstract}
We will create a web interface that enables users to list and find data from a set of films and associated information. This data will be stored within a server that the interface communicates with.

One part of the project will be to find suitable data from public sources and store this in a format that can be understood by software such as Jena. We will configure this software in an appropriate way so that it is able to read the stored data and provide this to other systems.

In a second step we will create and design a small web application, that uses an API of the software from step one to fetch data from the server. It will be possible to conduct simple search operations in that application which in turn communicates with the server API in order to find matching data.
\end{abstract}

\section{Introduction}
This document describes the authors' efforts to fulfill the tasks given in the assignment on the ``Semantic Web'' lecture. The assignment requests to create any kind of Ontology using RDF and make this available for reading and querying to users via a website.

\section{Creating Data}

\section{Data storage}

\section{Parsing and Displaying Data}

\section{The Search Interface}

\section{Conclusion}

\bibliographystyle{splncs}
\bibliography{documentation}
\end{document}
